rang: Reconstructing reproducible R computational environments

### 2023-03-02 paper/paper.qmd
Update the paper

>>>>

Similar to CRAN, Bioconductor is a series of repositories of R package for bioinformatics and computational biology. Also similar to CRAN, packages can get removed over time.

The Bioconductor package `Sushi` has been deprecated by the original authors and is removed from Bioconductor version 3.16 (2022-11-02). It is a data visualization tool for genomic data and was used in various online tutorials and papers, including the original paper announcing the package by the original authors [@phanstiel:2014:S].
